---
title: "Financial Health of Eye Care Practices Source Code"
subtitle: "CSC424 Final Project"
---

```{r setup, message=F, warning=F}
setwd("C:\\Repos\\Depaul\\CSC424\\Project\\")
library(gplots)
library(ca)
library(vcd)
library(FactoMineR)
library(factoextra)
library(corrplot)
library(yacca)
library(cluster)
library(GGally)
library(scales)
library(car)
library(QuantPsyc)
library(leaps)
library(psych)
```

# Data Cleaning

data prep has been consolidated into a single function so that it can be repeated throughout our analysis.

```{r dataPrep}
data_prep <- function() {
  ActualData <<- read.csv("practice_performance.csv", header=TRUE)
  RawPerformance <<- read.csv("practice_performance.csv", header=TRUE)
  
  count_pre_cleaning <- nrow(RawPerformance)

  # Requiring sales and receipts to be greater than zero
  RawPerformance <<- subset(RawPerformance, salesbyproviderall > 0)
  RawPerformance <<- subset(RawPerformance, salesbyproviderinsurance > 0)
  RawPerformance <<- subset(RawPerformance, salesbyproviderpatient > 0)
  RawPerformance <<- subset(RawPerformance, receiptsbyproviderall > 0)
  RawPerformance <<- subset(RawPerformance, receiptsbyproviderinsurance > 0)
  RawPerformance <<- subset(RawPerformance, receiptsbyproviderpatient > 0)
  count_after_cleaning_sales <- nrow(RawPerformance)
  
  # Requiring clinical events to be greater than zero.
  RawPerformance <<- subset(RawPerformance, eyeglasscaptureratebyorder > 0)
  RawPerformance <<- subset(RawPerformance, arcaptureratebyorder > 0)
  RawPerformance <<- subset(RawPerformance, contactlenscapturerate > 0)
  RawPerformance <<- subset(RawPerformance, medicalmanagementratio > 0)
  RawPerformance <<- subset(RawPerformance, ratio9921x > 0)
  RawPerformance <<- subset(RawPerformance, newpatientpercentage > 0)
  RawPerformance <<- subset(RawPerformance, productionbooked > 0)
  RawPerformance <<- subset(RawPerformance, productioncompleted > 0)
  count_after_cleaning_rates <- nrow(RawPerformance)

  # Require annual sales between 500k and 6000k
  RawPerformance <<- subset(RawPerformance, salesbyproviderall <= 1500000)
  RawPerformance <<- subset(RawPerformance, salesbyproviderall >= 125000)
  count_after_cleaning_annual <- nrow(RawPerformance)

  # Remove extreme receipts to sales ratios and very large accounts receivable
  RawPerformance <<- subset(RawPerformance, salesbyproviderinsurance/(receiptsbyproviderinsurance + 0.0001) < 5)
  RawPerformance <<- subset(RawPerformance, salesbyproviderinsurance/(receiptsbyproviderinsurance + 0.0001) > 0.2)
  RawPerformance <<- subset(RawPerformance, accountsreceivableall < salesbyproviderall * 1.5)
  count_after_cleaning_ledgers <- nrow(RawPerformance)

  # Building a summary of the rows removed so that we know the impact.
  DataRemoved <<- data.frame(step = "Remove Negative Dollar Rows", records = (count_pre_cleaning - count_after_cleaning_sales))
  DataRemoved <<- rbind(DataRemoved, data.frame(step = "Remove Zero-Value Rates", records = (count_after_cleaning_sales - count_after_cleaning_rates)))
  DataRemoved <<- rbind(DataRemoved, data.frame(step = "Remove Outlying Annual Revenue", records = (count_after_cleaning_rates - count_after_cleaning_annual)))
  DataRemoved <<- rbind(DataRemoved, data.frame(step = "Remove Outlying AR", records = (count_after_cleaning_annual - count_after_cleaning_ledgers)))
  DataRemoved <<- rbind(DataRemoved, data.frame(step = "Total Removed", records = (count_pre_cleaning - count_after_cleaning_ledgers)))

  # Fixing the ratio9921x so that it makes sense as a rate.
  ratio9921xdenominator <- RawPerformance$ratio9921xdenominator + RawPerformance$ratio9921xnumerator
  ratio9921x <- RawPerformance$ratio9921xnumerator / (ratio9921xdenominator + 0.0001)
  RawPerformance <<- subset(RawPerformance, select=-c(ratio9921x, ratio9921xdenominator))
  RawPerformance <<- cbind(RawPerformance, ratio9921x, ratio9921xdenominator)
  rm(ratio9921x, ratio9921xdenominator)
  
  # Count-based performance data
  CountPerformance <<- subset(RawPerformance, select=c(
    arcaptureratebyordernumerator,
    contactlenscaptureratenumerator,
    eyeglasscaptureratebyordernumerator,
    medicalmanagementrationumerator,
    newpatientpercentagenumerator,
    productionbookednumerator,
    patientage0to9,
    patientage10to19,
    patientage20to29,
    patientage30to39,
    patientage40to49,
    patientage50to59,
    patientage60to69,
    patientage70to79,
    patientage80to89,
    patientage90to99,
    patientgenderfemale,
    ratio9921xdenominator,
    ratio9921xnumerator,
    salesbyproviderinsurance,
    salesbyproviderpatient,
    receiptsbyproviderinsurance,
    receiptsbyproviderpatient,
    accountsreceivablecollections,
    accountsreceivableinsurance,
    accountsreceivablepatient
  ))
  
  # Rate-based performance data
  RatePerformance <<- subset(RawPerformance, select=c(
    arcaptureratebyorder,
    contactlenscapturerate,
    eyeglasscaptureratebyorder,
    medicalmanagementratio,
    newpatientpercentage,
    ratio9921x,
    salesbyproviderinsurance,
    salesbyproviderpatient,
    receiptsbyproviderinsurance,
    receiptsbyproviderpatient,
    accountsreceivablecollections,
    accountsreceivableinsurance,
    accountsreceivablepatient
  ))
  
  # Create demographic rates and add them to the data
  totalpatients <- RawPerformance$patientgenderfemale + RawPerformance$patientgendermale
  patientage0to9 <- RawPerformance$patientage0to9 / totalpatients
  patientage10to19 <- RawPerformance$patientage10to19 / totalpatients
  patientage20to29 <- RawPerformance$patientage20to29 / totalpatients
  patientage30to39 <- RawPerformance$patientage30to39 / totalpatients
  patientage40to49 <- RawPerformance$patientage40to49 / totalpatients
  patientage50to59 <- RawPerformance$patientage50to59 / totalpatients
  patientage60to69 <- RawPerformance$patientage60to69 / totalpatients
  patientage70to79 <- RawPerformance$patientage70to79 / totalpatients
  patientage80to89 <- RawPerformance$patientage80to89 / totalpatients
  patientage90to99 <- RawPerformance$patientage90to99 / totalpatients
  patientgenderfemale <- RawPerformance$patientgenderfemale / totalpatients
  patientgendermale <- RawPerformance$patientgendermale / totalpatients
  
  RatePerformance <<- cbind(RatePerformance,
                          patientage0to9,
                          patientage10to19,
                          patientage20to29,
                          patientage30to39,
                          patientage40to49,
                          patientage50to59,
                          patientage60to69,
                          patientage70to79,
                          patientage80to89,
                          patientage90to99,
                          patientgenderfemale,
                          totalpatients
  )
}
data_prep()
```

The following table shows the summary of the data being removed by the cleaning.

```{r dataPrepSummary}
DataRemoved
```

# Correspondence Analysis

```{r correspondence}
data_prep()
## Creating categorical variables from Patientage variables 
#First, combine patientage variables to create wider age groups
RawPerformance$patientage0to29 = RawPerformance$patientage0to9 + RawPerformance$patientage10to19 + RawPerformance$patientage20to29
RawPerformance$patientage30to59 = RawPerformance$patientage30to39 + RawPerformance$patientage40to49 + RawPerformance$patientage50to59
RawPerformance$patientage60to89 = RawPerformance$patientage60to69 + RawPerformance$patientage70to79 + RawPerformance$patientage80to89
RawPerformance$patientage90to119 = RawPerformance$patientage90to99 + RawPerformance$patientage100to109 + RawPerformance$patientage110to119

#Remove the original patientage variables (THIS IS OPTIONAL)
RawPerformance$patientage0to9 = NULL
RawPerformance$patientage10to19 = NULL
RawPerformance$patientage20to29 = NULL
RawPerformance$patientage30to39 = NULL
RawPerformance$patientage40to49 = NULL
RawPerformance$patientage50to59 = NULL
RawPerformance$patientage60to69 = NULL
RawPerformance$patientage70to79 = NULL
RawPerformance$patientage80to89 = NULL
RawPerformance$patientage90to99 = NULL
RawPerformance$patientage100to109 = NULL
RawPerformance$patientage110to119 = NULL

dim(RawPerformance)

# Let's check the mean counts of each patientage variable
summary(RawPerformance$patientage0to29)
summary(RawPerformance$patientage30to59)
summary(RawPerformance$patientage60to89)
summary(RawPerformance$patientage90to119)

# For each of the new patientage variables, if the number of patients (value in each cell) 
# is smaller than a certain value, replace it with a category
attach(RawPerformance)

RawPerformance$patientage0to29[patientage0to29 <= 500] = "Low" 
RawPerformance$patientage0to29[patientage0to29 > 500 & patientage0to29 <= 1000] = "Medium" 
RawPerformance$patientage0to29[patientage0to29 > 1000] = "High"

RawPerformance$patientage30to59[patientage30to59 <= 500] = "Low" 
RawPerformance$patientage30to59[patientage30to59 > 500 & patientage30to59 <= 1000] = "Medium" 
RawPerformance$patientage30to59[patientage30to59 > 1000] = "High"

RawPerformance$patientage60to89[patientage60to89 <= 500] = "Low" 
RawPerformance$patientage60to89[patientage60to89 > 500 & patientage60to89 <= 1000] = "Medium" 
RawPerformance$patientage60to89[patientage60to89 > 1000] = "High"

RawPerformance$patientage90to119[patientage90to119 <= 500] = "Low" 
RawPerformance$patientage90to119[patientage90to119 > 500 & patientage90to119 <= 1000] = "Medium" 
RawPerformance$patientage90to119[patientage90to119 > 1000] = "High"

detach(RawPerformance)

#Check frequencies of Low/Medium/High values in age variables
table(RawPerformance$patientage0to29)
table(RawPerformance$patientage30to59)
table(RawPerformance$patientage60to89)
table(RawPerformance$patientage90to119)

#Converting discrete numerical values (1,2,etc.) to characters
RawPerformance$patientgendermale = as.character(RawPerformance$patientgendermale)
RawPerformance$patientgenderfemale = as.character(RawPerformance$patientgenderfemale)

#Grouping the receipt amounts into categories based on the amount of receipt
attach(RawPerformance)
RawPerformance$receiptsall[receiptsbyproviderall <= 180000] = "Low" 
RawPerformance$receiptsall[receiptsbyproviderall > 180000 & receiptsbyproviderall <= 360000] = "Average" 
RawPerformance$receiptsall[receiptsbyproviderall > 360000 & receiptsbyproviderall <= 900000] = "High"
RawPerformance$receiptsall[receiptsbyproviderall > 900000 & receiptsbyproviderall] = "Very high"
detach(RawPerformance)


attach(RawPerformance)
t1 = table(receiptsall, patientage0to29)
t2 = table(receiptsall, patientage30to59)
t3 = table(receiptsall, patientage60to89)
t4 = table(receiptsall, patientage90to119)
detach(RawPerformance)

#Balloon plots
balloonplot(t1, main ="0-29 vs. Receipt", label = FALSE, show.margins = FALSE)
balloonplot(t2, main ="30-59 vs. Receipt", label = FALSE, show.margins = FALSE)
balloonplot(t3, main ="60-89 vs. Receipt", label = FALSE, show.margins = FALSE)
balloonplot(t4, main ="90-119 vs. Receipt", label = FALSE, show.margins = FALSE)


## Running Correspondence Analysis 
library(ca)

#CA on t1 
ca1 = ca(t1)
mosaic(t1, shade=TRUE, legend=TRUE) 

chisq1 = chisq.test(t1)
chisq1

#CA on t2
ca2 = ca(t2)
mosaic(t2, shade=TRUE, legend=TRUE) 

chisq2 = chisq.test(t2)
chisq2

#CA on t3 
ca3 = ca(t3)
mosaic(t3, shade=TRUE, legend=TRUE) 

chisq3 = chisq.test(t3)
chisq3

#CA on t4 
ca4 = ca(t4)
mosaic(t4, shade=TRUE, legend=TRUE) 

chisq4 = chisq.test(t4)
chisq4
```

# Cluster Analysis on Clinical Data

```{r clusterClinicalData}
data_prep()
set.seed(1024)
PairsSample <- sample(nrow(RawPerformance), nrow(RawPerformance)*0.25)

ClinicalData <- subset(RawPerformance, select=c(arcaptureratebyordernumerator, contactlenscaptureratedenominator, contactlenscaptureratenumerator, eyeglasscaptureratebyorderdenominator, eyeglasscaptureratebyordernumerator, medicalmanagementrationumerator, newpatientpercentagenumerator, ratio9921xnumerator, ratio9921xdenominator));
ClinicalData = log1p(ClinicalData)
fviz_nbclust(ClinicalData, clara, method="wss", k.max=10, nboot=25) + theme_classic()

set.seed(1024)
ClinicalDataCluster <- clara(ClinicalData, 5, metric="manhatten", samples=50, pamLike=TRUE)
fviz_cluster(ClinicalDataCluster, ellipse.type="t", geom="point", pointsize=1, ggtheme = theme_classic())

ClinicalDataVisual <-cbind(ClinicalData, ClinicalDataCluster$clustering)
colnames(ClinicalDataVisual) <- c('AR Add', 'CL Rx', 'CL Sale', 'EG Rx', 'EG Sale', 'Med', 'New Pat', '99214', '99213', 'Cluster')
ClinicalDataVisual$Cluster <- as.factor(ClinicalDataVisual$Cluster)
ggpairs(ClinicalDataVisual[PairsSample,], lower=list(combo=wrap("facethist", binwidth=1), mapping=ggplot2::aes(color=Cluster)))

ClinicalDataMedoids <- cbind(percent(ClinicalDataCluster$clusinfo[,1]/nrow(ClinicalData)), expm1(ClinicalDataCluster$medoids))
rownames(ClinicalDataMedoids) <- c('(1) High Capture Up-Coding', '(2) Up-Coding', '(3) Low Capture Up-Coding', '(4) Low Capture', '(5) Low Capture Under-Coding')
colnames(ClinicalDataMedoids) <- c('Cluster Size', 'AR Add', 'CL Rx', 'CL Sale', 'EG Rx', 'EG Sale', 'Med', 'New Pat', '99214', '99213')
ClinicalDataMedoids
```

# Cluster Analysis on Patient Demographics

```{r clusterDemographics}
data_prep()
set.seed(1024)

#### Use Rate Performance
patients_rate = subset(RatePerformance, select = c(patientage0to9,
                                             patientage10to19,
                                             patientage20to29,
                                             patientage30to39,
                                             patientage40to49,
                                             patientage50to59,
                                             patientage60to69,
                                             patientage70to79,
                                             patientage80to89,
                                             patientage90to99
                                             
))


# Find number of K
fviz_nbclust(patients_rate, clara, method = "wss", k.max = 6, nboot = 25 + theme_classic())

# Kmean Clustering: after several attempts, I find out that k =3 is the best fit amount for clusters.



#*************************************************
#Performing CLARA analysis:
patient_cluster = clara(patients_rate, 3, metric = 'manhattan', samples = 50, pamLike = T)
patient_cluster

#Visualization for data distribution:
fviz_cluster(patient_cluster, geom = 'point', ellipse.type = 't',
             palette = 'jco', ggtheme = theme_classic())

# Correlation Table - GGpairs
patient_r.Vis = cbind(patients_rate,patient_cluster$clustering)
colnames(patient_r.Vis) =  c('Patient0-9', 'Patient10-19','Patient20-29','Patient30-39',
                             'Patient40-49', 'Patient50-59', 'Patient60-69','Patient70-79',
                             'Patient80-89', 'Patient90-99',"Cluster")

patient_Vis = as.data.frame.matrix(patient_r.Vis)

patient_Vis$Cluster = as.factor(patient_Vis$Cluster)

ggpairs(patient_Vis, lower = list(combo = wrap("facethist", binwidth = 0.1),
                                    mapping=ggplot2::aes(color=Cluster)))

```

# Hierarchical Clustering on Principal Components

```{r clusterHierarchical}
#Automate - Tree Build
HCPC(patients_rate, nb.clust = -1, min = 3, max = NULL, graph = TRUE)

#Continuous Hirachical

#PCA analysis
patient.pca = PCA(patients_rate, ncp = 4, graph = F)
fviz_pca_var(patient.pca)

# Apply Clustering
patient.hc = HCPC(patient.pca, graph = F)

# Map Visualization
fviz_cluster(patient.hc, main = 'Factor Map')
```

# Principal Component Analysis and Common Factor Analysis

```{r pca}
data_prep()
CountPerformance=log1p(CountPerformance)
colSums(is.na(CountPerformance))

#Missing values are Replaced With Mean

which(is.na(CountPerformance$accountsreceivablepatient))

CountPerformance$accountsreceivablepatient[which(is.na(CountPerformance$accountsreceivablepatient))]=9.775

dim(CountPerformance)
dim(RatePerformance)


#KMO and Bartlett tets are performed on the Count and rate Performance and it gives good results to continue analysis

bartlett.test(CountPerformance)
KMO(CountPerformance)
bartlett.test(RatePerformance)
KMO(RatePerformance)


## Analysis on the CountPerformance

## Checking VIF among the variables and variables with high VIF values will be removed.

predVars_Count <- subset(CountPerformance, select=-c(eyeglasscaptureratebyordernumerator))
corrplot(cor(predVars_Count), method="number")
library(mctest)
imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)

##Patient gender female has high VIF and also since it is highly correlated with other variables, we can explain its 
##variance with the help of other variables even if it is not present. The same Process continues until all the Variables with higher VIF values are taken out. 

predVars_Count$patientgenderfemale=NULL


imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

predVars_Count$receiptsbyproviderpatient=NULL

imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

predVars_Count$patientage60to69=NULL

imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

predVars_Count$patientage40to49=NULL

imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

predVars_Count$patientage70to79=NULL

imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

predVars_Count$patientage30to39=NULL

imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

predVars_Count$patientage50to59=NULL

imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

predVars_Count$patientage80to89=NULL

imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

predVars_Count$patientage10to19=NULL

imcdiag(predVars_Count, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Count),method="number")

## After all these steps still patientage20to29 and salesbyproviderinsurance variables has VIF just above than 5 and In
## the correlation matrix these variables are highly correlated with only 4 variables out of 16. So we can keep the variables for analysis.


# In this section i checked for the significant correlations(PCA Assumption) in the variables. In CountPerformance every variable has significant correlation
# with all other variables. Usually if one variables has significant correlations with most of other variables it may result in one component(having one variable variance) so its better to
## take it out from the analysis. But in this case all variables has significant correlations with other so one component doen't have the variance of one variable.

MCorrTest = corr.test(predVars_Count, adjust="none")
M = MCorrTest$p
MTest = ifelse(M < .01, T, F)
colSums(MTest) - 1


#PCA and CFA analysis on CountPerformance

pca_count=prcomp(predVars_Count,scale. = T,center = T)
plot(pca_count)
abline(1,0)

summary(pca_count)

# By kaiser and screeplot method we can determine either 2 or 3 components respectively.

#with 2 components

rc_count_2comp=psych::principal(predVars_Count,nfactors = 2,rotate = "varimax")
print(rc_count_2comp$loadings,cutoff=.4,sort=T)

#CFA with 2 Components on Count Performance

fc_count_2comp=factanal(predVars_Count,2)
print(fc_count_2comp$loadings,cutoff=.4,sort=T)

# with 3 components
rc_count_3comp=psych::principal(predVars_Count,nfactors = 3,rotate = "varimax")
print(rc_count_3comp$loadings,cutoff=.4,sort=T)

fc_count_3comp=factanal(predVars_Count,3)
print(fc_count_3comp$loadings,cutoff=.4,sort=T)

#Analysis on RatePerformance

## Checking VIF among RatePerformance Variables

predVars_Rate=RatePerformance
corrplot(cor(predVars_Rate), method="number")
imcdiag(predVars_Rate, CountPerformance$eyeglasscaptureratebyordernumerator)

predVars_Rate$receiptsbyproviderpatient=NULL

imcdiag(predVars_Rate, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Rate), method="number")

predVars_Rate$totalpatients=NULL

imcdiag(predVars_Rate, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Rate), method="number")

predVars_Rate$patientage60to69=NULL

imcdiag(predVars_Rate, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Rate), method="number")

predVars_Rate$patientage70to79=NULL

imcdiag(predVars_Rate, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Rate), method="number")

predVars_Rate$patientage80to89=NULL

imcdiag(predVars_Rate, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Rate), method="number")

predVars_Rate$receiptsbyproviderinsurance=NULL

imcdiag(predVars_Rate, CountPerformance$eyeglasscaptureratebyordernumerator)
corrplot(cor(predVars_Rate), method="number")

##Checking for Significant Correlations

MCorrTest = corr.test(predVars_Rate, adjust="none")
M = MCorrTest$p
MTest = ifelse(M < .01, T, F)
colSums(MTest) - 1

##PCA and CFA on RatePerformance

pca_rate=prcomp(predVars_Rate,scale. = T,center = T)
plot(pca_rate)
abline(1,0)
summary(pca_rate)

# By screeplot we can take either 3 or 4 components and by kaiser method 6 components are required. So we check analysis with 3,4,5,6 no.of components

# PCA with 3 components

rc_rate_3comp=psych::principal(predVars_Rate,nfactors = 3,rotate = "varimax")
print(rc_rate_3comp$loadings,cutoff=.4,sort=T)

## CFA with 3 components

fc_rate_3comp=factanal(predVars_Rate,3)
print(fc_rate_3comp$loadings,cutoff=.4,sort=T)


# PCA with 4 components

rc_rate_4comp=psych::principal(predVars_Rate,nfactors = 4,rotate = "varimax")
print(rc_rate_4comp$loadings,cutoff=.4,sort=T)

## CFA with 4 components

fc_rate_4comp=factanal(predVars_Rate,4)
print(fc_rate_4comp$loadings,cutoff=.4,sort=T)


# PCA with 5 components

rc_rate_5comp=psych::principal(predVars_Rate,nfactors = 5,rotate = "varimax")
print(rc_rate_5comp$loadings,cutoff=.4,sort=T)

## CFA with 5 components

fc_rate_5comp=factanal(predVars_Rate,5)
print(fc_rate_5comp$loadings,cutoff=.4,sort=T)

# PCA with 6 components

rc_rate_6comp=psych::principal(predVars_Rate,nfactors = 6,rotate = "varimax")
print(rc_rate_6comp$loadings,cutoff=.4,sort=T)

## CFA with 6 components

fc_rate_6comp=factanal(predVars_Rate,6)
print(fc_rate_6comp$loadings,cutoff=.4,sort=T)
```

# Canonical Correlation Analysis

```{r cca}
data_prep()

#Rebuild the PCA data we are pulling the variables from
PCARates <- subset(RatePerformance, select=c(arcaptureratebyorder, contactlenscapturerate, eyeglasscaptureratebyorder, medicalmanagementratio, newpatientpercentage, ratio9921x, salesbyproviderinsurance, salesbyproviderpatient, accountsreceivablecollections, accountsreceivableinsurance, accountsreceivablepatient, patientage0to9, patientage10to19, patientage20to29, patientage30to39, patientage40to49, patientage90to99))
PCARates <- log1p(PCARates)
PCARates$salesbyproviderinsurance <- log1p(PCARates$salesbyproviderinsurance)
PCARates$salesbyproviderpatient <- log1p(PCARates$salesbyproviderpatient)
PCARates$accountsreceivablecollections <- log1p(PCARates$accountsreceivablecollections)
PCARates$accountsreceivableinsurance <- log1p(PCARates$accountsreceivableinsurance)
PCARates$accountsreceivablepatient <- log1p(PCARates$accountsreceivablepatient)
PCARates <- na.omit(PCARates)

#Break the data into the x and y variables
CorePatientData <- subset(PCARates, select=c(medicalmanagementratio, newpatientpercentage, patientage20to29, patientage30to39, patientage40to49, patientage90to99))
RevenueData <- subset(PCARates, select=c(salesbyproviderinsurance, salesbyproviderpatient, accountsreceivableinsurance, accountsreceivablepatient))
YoungPatientData <- subset(PCARates, select=c(arcaptureratebyorder, patientage0to9, patientage10to19))
CaptureData <- subset(PCARates, select=c(contactlenscapturerate, eyeglasscaptureratebyorder))

#Perform the CCA
CorePatientVSCapture <- cca(CorePatientData, CaptureData)

#Test the CCA Significance
F.test.cca(CorePatientVSCapture)

#Variates
CorePatientVSCapture$xcoef[,1:2]
CorePatientVSCapture$ycoef[,1:2]

#Loadings
CorePatientVSCapture$xstructcorr[,1:2]
CorePatientVSCapture$ystructcorr[,1:2]

#Helio plots of the variates
helio.plot(CorePatientVSCapture, x.name="Core Patient Data", y.name="Capture Rate", xvlab=c('Medical', 'New Patient', 'Age 20-29', 'Age 30-39', 'Age 40-49', 'Age 90-99'), yvlab=c('Contact Lens', 'Eyeglass'))
helio.plot(CorePatientVSCapture, x.name="Core Patient Data", y.name="Capture Rate", xvlab=c('Medical', 'New Patient', 'Age 20-29', 'Age 30-39', 'Age 40-49', 'Age 90-99'), yvlab=c('Contact Lens', 'Eyeglass'), cv=2)
```

# R Version and Required Libraries

```{r versionInfo}
R.version
packageVersion("gplots")
packageVersion("ca")
packageVersion("vcd")
packageVersion("FactoMineR")
packageVersion("factoextra")
packageVersion("corrplot")
packageVersion("yacca")
packageVersion("cluster")
packageVersion("GGally")
packageVersion("scales")
packageVersion("car")
packageVersion("QuantPsyc")
packageVersion("leaps")
packageVersion("psych")
```